Experiences in teaching with Jupyter, Jupyterhub, and nbgrader

### 2019-09-24 paper/paper.tex
collaboration intro -

>>>>

\section{Introduction new technologies in teaching in mutual collaboraion}

Back in 2017 the collaboration between three partners University of
Augsburg, European University Cyprus and University of Silesia has
been initiated in the form of Erasmus+ project. The general aim was to
research on possibility of implementing good practices in using Python
programming language and Jupyter notebook in teaching in different
environments. Experience among parters with both Python and Jupyter
were diversified. It opened a possibility to observe a process of an
adotion of new educatioal approach at different phases at the same
time.

The collaboration consisted on three elements: creation of software
infrastructure, authoring course materials and experimenting with
elements of Test Driven Development process using nbgrader.

\texttt{Description of each partner specifics}
